\textbf{Manual Coding Guidelines\\[0.15cm] for Automation Patents}

### 2015-10-23 manual_coding_guidelines/manual_coding_guidelines.tex
Parenthesis

\begin{frame}\frametitle{The column ``Highly uncertain"}
\begin{itemize}
	\item If you're highly doubtful if you made the right decision, please enter 1 into the column ``Highly uncertain". If you're sure, you don't need to enter a 0.
	\item Even if your not sure and you write a 1 to "Highly uncertain" please still make the decisions on whether the patent is an automation patent and whether it is manual or cognitive.
	\item So far, we classified around 9\% of patents that we manually coded as "Highly uncertain".
\end{itemize}
\end{frame}

>>>>

\begin{frame}\frametitle{The column ``Highly uncertain"}
\begin{itemize}
	\item If you're highly doubtful if you made the right decision, please enter 1 into the column ``Highly uncertain". If you're sure, you don't need to enter a 0.
	\item Even if your not sure and you write a 1 to ``ighly uncertain" please still make the decisions on whether the patent is an automation patent and whether it is manual or cognitive.
	\item So far, we classified around 9\% of patents that we manually coded as ``Highly uncertain".
\end{itemize}
\end{frame}
